Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-04-27 overleaf/prob_stmt_np_hardness.tex
Finished pass on Analytical model section.

\ana{This paragraph needs work.} To formalize the reduction, suppose $P$ is a schedule with minimal cost (computed by a black-box algorithm). 
%We can derive a schedule $P'$ with the same cost as $P$, by mapping each mixed node $P_i \in P$ to two consecutive nodes in $P'$: an $A$-instruction node followed by an $M$-instruction node. 
Clearly, $P'$, which now is a sequence of $M_1$ and $M_2$ nodes, is a supersequence of each sequence $S_i$, i.e., $P'$ is a common supersequence of $S_1 \dots S_n$. It is also a shortest common supersequence. 
%To see this, let $X$ and $Y$ denote, respectively, the number of $A$ and $M$ nodes in $P'$. 
The cost of $P$, is $L\alpha_\mathit{fix}+N\alpha_\mathit{var}$ where $L$ is the length of $P$ and $N$ is the total number of instructions across all sequences. %$X \cdot \alpha + Y \cdot \beta$.

Now suppose, there exists a shorter common supersequence $P'$. 
that consists of $X'$ nodes of type $A$-instructions $Y'$ nodes of type $M$-instructions. Since $P''$ is shorter than $P'$, therefore $X' + Y' < X + Y$, and $X' \cdot \alpha + Y' \cdot \beta < X \cdot \alpha + Y \cdot \beta$ i.e. $\mathit{cost}(P'') < \mathit{cost}(P')$. But $\mathit{cost}(P') = \mathit{cost}(P)$ and $\mathit{cost}(P)$ is the optimal cost.  Therefore $\mathit{cost}(P'') < \mathit{cost}(P')$ is contradiction and no such $P''$ exists. \qed

>>>>

To formalize the reduction, suppose $P$ is a schedule with minimal cost (computed by a black-box algorithm). 
%We can derive a schedule $P'$ with the same cost as $P$, by mapping each mixed node $P_i \in P$ to two consecutive nodes in $P'$: an $A$-instruction node followed by an $M$-instruction node. 
Clearly, $P$, which now is a sequence of $M_1$ and $M_2$ nodes, is a supersequence of each sequence $S_i$, i.e., $P$ is a common supersequence of $S_1 \dots S_n$. It is also a shortest common supersequence. 
%To see this, let $X$ and $Y$ denote, respectively, the number of $A$ and $M$ nodes in $P'$. 
The cost of $\mathit{cost}(P) = L\alpha_\mathit{fix}+N\alpha_\mathit{var}$ where $L$ is the length of $P$ and $N$ is the total number of instructions across all sequences. %$X \cdot \alpha + Y \cdot \beta$. 
Now suppose, there exist a shorter common supersequence $P'$ of length $L'$. $\mathit{cost}(P') < \mathit{cost}(P)$ since $L'\alpha_\mathit{var} + N\alpha_\mathit{var} < L\alpha_\mathit{var} + N\alpha_\mathit{var}$, however, this is a contradiction to the assumption that $P$ has the lowest cost. \qed
%that consists of $X'$ nodes of type $A$-instructions $Y'$ nodes of type $M$-instructions. Since $P''$ is shorter than $P'$, therefore $X' + Y' < X + Y$, and $X' \cdot \alpha + Y' \cdot \beta < X \cdot \alpha + Y \cdot \beta$ i.e. $\mathit{cost}(P'') < \mathit{cost}(P')$. But $\mathit{cost}(P') = \mathit{cost}(P)$ and $\mathit{cost}(P)$ is the optimal cost.  Therefore $\mathit{cost}(P'') < \mathit{cost}(P')$ is contradiction and no such $P''$ exists. \qed
